\newpage
\thispagestyle{empty}

\begin{center}

\huge{Abstract}\\[0.5cm]
\normalsize
\textsc Automatic Face Recognition Technologies have seen dramatic improvements in performance over the past
years and such systems are now widely used for security and commercial applications. An automated system for human
face recognition in a real time background for a company to mark the attendance of the employees.
So smart Attendance using Real Time Face Recognition is a real world solution which comes with day to day activities
of handling employees. The task is very difficult as the real time background subtraction in an image is still a challenge.
To detect real time human face are used to recognize the face detected with a high accuracy rate. The matched face is
used to mark attendance of the employee.
Our system maintains te attendance records of employees automatically. Manual Entering of in logbooks becomes a
difficult task and it also wastes the time. So we designed an efficient module that comprises of face recognition to manage
the attendance records of employees. Our module enrolls the staff ’s face. This enrolling is a onetime process and their
face will be stored in the database. During enrolling of face we require a system since it is a onetime process. You can
have your own roll number as your employee id which will be unique for each employee.
The presence of each employee will be updated in a database. The results showed improved performance over manual
after employee identification. This product gives much more solutions with accurate results in user interactive manner
rather than existing attendance and leave management system.

\\[2.0cm]

\end{center}
\normalsize 



